Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-21 cbm-rbd-paper.tex
post pred start

In place of the usual parametrization in terms of $a_k$ and $b_k$,
we use the parameters $\nkz > 1$ and $\ykz > 0$
because they have a simple interpretation.
They are defined as
\begin{align}
\nkz &= a_k - 1 & &\text{ and}
&
\ykz &= b_k / \nkz,
\label{eq:abtony}
\end{align}
where $\ykz$ can be interpreted as the prior guess for the scale parameter $\lambda_k$,
as $\E[\lambda_k\mid\nkz,\ykz] = \ykz$.
Using \eqref{eq:lambdainterpret},
we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\ykz$.
$\nkz$ can be seen as a prior strength or pseudocount,
this will become clear in the discussion of the update step below.

The parametrization in terms of $\nkz$ and $\ykz$ also clarifies the nature of the combination
of prior information and data through Bayes' rule.
In the conjugate setting,
applying Bayes' rule simply means that the prior parameters $\nkz$ and $\ykz$
are updated to posterior parameters, which we denote by $\nkn$ and $\ykn$, respectively.
Assume we observe $n_k = e_k + c_k$ component lifetimes,
where $e_k$ is the number of actual failure events,
and $c_k$ is the number of right-censored observations.
We denote the failure times by $t_{k,1}, \ldots, t_{k,e_k}$,
and the censoring times by $t^+_{k,1}, \ldots, t^+_{k,c_k}$,
and collect them in an observation vector $\vec{t}_k = (t_{k,1}, \ldots, t_{k,e_k}, t^+_{k,1}, \ldots, t^+_{k,c_k})$.
Then, the updated, posterior parameters are
\begin{align}
\nkn &= \nkz + e_k\,, 
&
\ykn &=  \frac{\nkz \ykz + \tautk}{\nkz + e_k}\,,
\label{eq:ig-update}
\end{align}
where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.

@@

\section{Posterior predictive***}

For this, we need the posterior predictive distribution
of the number of components that function at times $t > \tnow$,
which we will derive .

>>>>

In place of the usual parametrization in terms of $a_k$ and $b_k$,
we use the parameters $\nkz > 1$ and $\ykz > 0$
(the upper index ${}\uz$ is used to indicate that these are prior parameters)
because they have a simple interpretation.
They are defined as
\begin{align}
\nkz &= a_k - 1 & &\text{ and}
&
\ykz &= b_k / \nkz,
\label{eq:abtony}
\end{align}
where $\ykz$ can be interpreted as the prior guess for the scale parameter $\lambda_k$,
as $\E[\lambda_k\mid\nkz,\ykz] = \ykz$.
Using \eqref{eq:lambdainterpret},
we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\ykz$.
$\nkz$ can be seen as a prior strength or pseudocount,
this will become clear in the discussion of the update step below.

The parametrization in terms of $\nkz$ and $\ykz$ also clarifies the nature of the combination
of prior information and data through Bayes' rule.
In the conjugate setting,
applying Bayes' rule simply means that the prior parameters $\nkz$ and $\ykz$
are updated to posterior parameters, which we denote by $\nkn$ and $\ykn$, respectively.
Assume we observe $n_k = e_k + c_k$ component lifetimes,
where $e_k$ is the number of actual failure events,
and $c_k$ is the number of right-censored observations.
We denote the failure times by $t_{k,1}, \ldots, t_{k,e_k}$,
and the censoring times by $t^+_{k,1}, \ldots, t^+_{k,c_k}$,
and collect them in an observation vector $\vec{t}_k = (t_{k,1}, \ldots, t_{k,e_k}, t^+_{k,1}, \ldots, t^+_{k,c_k})$.
Then, the updated, posterior parameters are
\begin{align}
\nkn &= \nkz + e_k\,, 
&
\ykn &=  \frac{\nkz \ykz + \tautk}{\nkz + e_k}\,,
\label{eq:ig-update}
\end{align}
where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.
The upper index ${}\un$ indicates that these are posterior parameters resulting from an update with $n_k$ observations,
where we leave out the index $k$ for $n_k$ in the upper index to increase legibility.

@@

***An example for the survival signature for the system in Figure *** is given in Table ****.

\section{Component posterior predictive distributions***}
\label{sec:postpred}

To calculate the current system reliability curve,
we thus need the probabilities $P(C^k_t = l_k)$,
which give the number of components that function at times $t > \tnow$.
In our Bayesian framework, these probabilities are given
by a so-called predictive distribution that can be derived from the distribution over $\lambda$.
This distribution needs to account for expert knowledge and test data;
following our comment at the end of Section~\ref{sec:weibull},
we assume here that ***change notation to $n_k^{(\text{test})}$ and $n_k^{(\text{now})}$???

but also for the information gained from the current run of the system:
both failure times of components (if any)
and the right-censoring time $\tnow$ for each non-failed component in the system
can be used to update $\nkz$ and $\ykz$.

In analogue to the notation from Section~\ref{sec:weibull},
let $n_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
We can thus collect these observations, as of $\tnow$, in a vector
$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
containing $n_c$ right-censored obsevations $\tpnow$.

Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
must be used when calculating the posterior predictive distribution.
